problem years

### 2024-08-13 src/oa_RF_corrected.Rmd
LAD lisa
oa lisa

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  #assign(paste0("model.all",as.character(i)), model.all)

  #file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_", as.character(i), ".RData")
  file <- paste0("/hdd/tmp/regions/corrected/regions_corrected_", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

>>>>

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

  file <- paste0("/hdd/tmp/regions/corrected/regions_corrected_", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

### 2024-08-13 src/oa_RF_corrected_10.Rmd
LAD lisa
oa lisa

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  #assign(paste0("model.all",as.character(i)), model.all)

  #file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_corrected_", as.character(i), ".RData")
  file <- paste0("/hdd/tmp/regions/corrected_10/regions_corrected_10", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

@@

>>>>

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

  file <- paste0("/hdd/tmp/regions/corrected_10/regions_corrected_10", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

@@

The corrected for n = 1 makes sense. Check the name changes below.

### 2024-08-13 src/problem_years.Rmd
oa lisa

# theme(axis.text.x = element_blank(),
#       axis.text.y = element_blank(),
#       axis.ticks = element_blank(),
#       rect = element_blank())

@@

### lisa map legend
```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/LA/lisa_level_pc", n, "_la_legend.png") 
legend <- ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  scale_fill_manual(values = palette_new, na.value="white", drop = F, name = NULL) +
  theme_minimal() +
  theme(legend.position="right",
        legend.margin=ggplot2::margin(c(1,1,1,1)))

@@

  #spatial weight matrix
  #moved out of the loop

@@

  cities <- maps::world.cities %>%
    filter(country.etc=="UK") %>% 
    arrange(pop) %>% tail(10) 
  tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

  ggplot(data = oa.uk, aes(fill = quadr$median)) +
    geom_sf(data = uk, fill = "white", linewidth = .5) +
    geom_sf(linewidth = 0) +
    geom_sf(data = tif_sf, fill = "black", size = .3) +
    #geom_sf_text(data = tif_sf, aes(label = name, fill = "black"), size = 4) +
    scale_fill_manual(values = palette_new, na.value="white", drop = F) +
    theme_minimal() +
    theme(panel.grid.major = element_line(colour = "transparent"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.title=element_blank()) +
          #legend.position="none") +
    guides(fill = guide_legend(reverse = TRUE)) +
    labs(title = t,
        subtitle = "LISA, websites per OA")

>>>>

@@

### lisa map legend

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/LA/lisa_level_pc", n, "_la_legend.png") 
legend <- ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  scale_fill_manual(values = palette_new, na.value="white", drop = F, name = NULL) +
  theme_minimal() +
  theme(legend.position="right",
        legend.margin=ggplot2::margin(c(1,1,1,1)))

@@

@@

  # cities <- maps::world.cities %>%
  #   filter(country.etc=="UK") %>% 
  #   arrange(pop) %>% tail(10) 
  # cities <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

  ggplot(data = oa.uk, aes(fill = quadr$median)) +
    geom_sf(data = uk, fill = "white", linewidth = .5) +
    geom_sf(linewidth = 0) +
    #geom_sf(data = cities, fill = "black", size = .3) +
    #geom_sf_text(data = cities, aes(label = name, fill = "black"), size = 4) +
    scale_fill_manual(values = palette_new, na.value="white", drop = F) +
    theme_minimal() +
    theme(panel.grid.major = element_line(colour = "transparent"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none") +
    #guides(fill = guide_legend(reverse = TRUE)) +
    labs(title = paste0("OA, ", t)) +
    theme(legend.title=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        plot.title = element_text(hjust = 0.5)) +
    theme(plot.title = element_text(size=20, face = "bold"))
